### 2023-10-02 3.Design/memcell.tex
Changed circuit's ref
worked on area
Changed pins

The circuit is shown in \cref{fig:memcellCircuit}. The value/voltage is trapped in the capacitor using \ac{CMOS} switches.

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{memcell/memCircuit}
  \caption{Memory cell circuit}
  \label{fig:memcellCircuit}
\end{figure}

@@

With $A_{CMOS} = w\cdot l = 9\cdot 10^{-7} \cdot 6 \cdot 10^{-8} = 5.4 \cdot 10^{-14} m^2$ TODO check value w et l

@@

\begin{figure}[H]
  \centering
  \includesvg[height=2.5cm]{memcell/memcellSymbol}
  \caption{Memory cell symbol with the input pin (left), the output pin (right), the input enable pin (top) and the output enable pin (bottom)}
  \label{fig:memcellCircuit}
\end{figure}

>>>>

The circuit is shown in \cref{circt:memcell}. The value/voltage is trapped in the capacitor using \ac{CMOS} switches.

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{memcell/memCircuit}
  \caption{Memory cell circuit}
  \label{circt:memcell}
\end{figure}

@@

With $A_{CMOS} = w\cdot l = 2\cdot 10^{-7} \cdot 6 \cdot 10^{-8} = 1.2 \cdot 10^{-14} m^2$

@@

\begin{figure}[H]
  \centering
  \includesvg[height=2.5cm]{memcell/memcellSymbol}
  \caption{Memory cell symbol with the input enable pin (top) and the output enable pin (bottom). The left and right pins are interchangebly the input and ouput for the sake of readability}
  \label{circt:memcell}
\end{figure}
